Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-10 paper.Rmd
Tue Jan 10 22:00:10 CET 2023: update-remote.sh

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv",
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character")
)

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c",
 caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=FALSE ) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

>>>>

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit_mean.csv",
  # "/Users/rmn/github/master_thesis/data/summary_table_final_fit_median.csv",  -> Use this path to summarize by median
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character")
)

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c"
 #caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=FALSE ) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

### 2023-01-10 slides.Rmd
Tue Jan 10 22:00:10 CET 2023: update-remote.sh

---
title: "Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming"
subtitle: "Kolloquium zur Masterarbeit im M.Sc. Wirtschaftspädagogik "
author: "Roman Hoehn"
institute: "Johannes Gutenberg-Universität Mainz"
date: "Datum: 25.01.2023"
fontsize: 11pt
link-citations: true
output:
  beamer_presentation:
    # color: "beaver"
    # theme: "Szeged"
    # fonttheme: "structurebold"
    # fig_width: 7
    # fig_height: 5
    # keep_tex: true
    fig_caption: no
    number_sections: true
    slide_level: 2
toc: yes
bibliography: ref/ref.bib
csl: csl/harvard-cite-them-right.csl
includes:
      in_header: [header_files/slides.tex]
---

>>>>

---
#title: "Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming"
subtitle: "Kolloquium zur Masterarbeit im M.Sc. Wirtschaftspädagogik "
author: "Roman Hoehn"
institute: "Johannes Gutenberg-Universität Mainz"
date: "Datum: 25.01.2023"
fontsize: 11pt
link-citations: true
output:
  beamer_presentation:
    theme: "Madrid"
    fonttheme: "structurebold"
    fig_width: 12
    fig_height: 10
    # keep_tex: true
    fig_caption: no
    number_sections: true
    slide_level: 2
toc: yes
bibliography: ref/ref.bib
csl: csl/harvard-cite-them-right.csl
includes:
      in_header: [header_files/slides.tex]

---
